The Forward March of Categorical Tolerance in the United States?

### 2025-06-07 analysis-old.qmd
buncha stuff

```{r Data Wrangling}
    dat.dis <- dat.genres(dat)$dat.g %>%
          mutate(across(Classical:Metal, function(x) {if_else(x < 3, 1, 0)})) %>% 
          rowwise() %>% 
          mutate(num.dis = sum(c_across(Classical:Metal), na.rm = T)) %>% 
          ungroup() %>% 
          mutate(bin.dis = if_else(num.dis == 0, 1, 0))
    head(dat.dis)
         reg.dat <- dat.demog(dat) %>% 
          left_join(dat.dis) %>% 
          rename(Survey_Year = year, Political_Ideology = polviews, Education = Educ) %>%
          mutate(Black = if_else(Race == "Black", 1, 0)) %>% 
          mutate(Hisp = if_else(Race == "Hisp.", 1, 0)) %>% 
          mutate(Asian = if_else(Race == "Asian", 1, 0)) %>% 
          mutate(White = if_else(Race == "White", 1, 0)) %>%
          mutate(Mult = if_else(Race == "Mult.", 1, 0)) %>% 
          mutate(Native = if_else(Race == "Native/Other", 1, 0)) %>% 
          mutate(Woman = if_else(Gender == "Woman", 1, 0)) %>% 
          mutate(Age.n = as.numeric(Age)) %>% 
          mutate(Young = if_else(Age.n > 1 & Age.n < 5, 1, 0)) %>% 
          mutate(Old = if_else(Age.n > 9, 1, 0)) %>% 
          mutate(Educ.n = as.numeric(Education)) %>% 
          mutate(Low.Educ = if_else(Educ.n == 1, 1, 0)) %>% 
          mutate(Mid.Educ = if_else(Educ.n == 2 | Educ.n == 3, 1, 0)) %>% 
          mutate(Hi.Educ = if_else(Educ.n == 4, 1, 0)) %>% 
          mutate(polviews.n = as.numeric(Political_Ideology)) %>% 
          mutate(Moderate = if_else(polviews.n == 3 | polviews.n == 4, 1, 0)) %>% 
          mutate(Survey_Year = factor(Survey_Year, labels = c("2021", "2023", "2023"))) %>% 
          mutate(Age = factor(Age, 
                             labels = c("18 - 19", "20 - 24",
                                        "25 - 29", "30 - 34", "35 - 39", "40 - 44",
                                        "45 - 49", "50 - 54", "55 - 59", "60 - 64",
                                        "65 - 69", "70+"))) %>% 
         mutate(Education = factor(Education, labels = c("High School", "Associate", "Bachelor", "Grad/Prof."))) %>% 
         mutate(Political_Ideology = factor(Political_Ideology, 
                             labels = c("Extremely liberal", "Liberal",
                              "Slightly liberal", "Moderate",
                              "Slightly conservative", "Conservative")))
```

@@

# Regression
```{r Regression Analysis}
     m1 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult + Survey_Year, 
       data = reg.dat
       )
     m2 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult + Survey_Year, 
       data = reg.dat, weights = weight
       )
     m3 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult,       
       data = reg.dat.21, weights = weight
       )
     m4 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult,       
       data = reg.dat.23, weights = weight
       )
     m5 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult,       
       data = reg.dat.21
       )
     m6 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult,       
       data = reg.dat.23
       )
     tab_model(m1, m2, transform = NULL, 
               file = here("Tabs", "zinf-reg.html"), 
               auto.label = TRUE, dv.labels = c("Unweighted", "Weighted"), 
               CSS = list(css.table = 'font-size: 12px;',
                          css.td = 'border-bottom: 0px;'), 
               show.zeroinf = TRUE, show.ci = FALSE)
     tab_model(m5, m3, m6, m4, transform = NULL, 
               file = here("Tabs", "zinf-reg-appendix.html"), 
               auto.label = TRUE, dv.labels = 
                 c("Unweighted (2021)", "Weighted (2021)", 
                   "Unweighted (2023)", "Weighted (2023)"), 
               CSS = list(css.table = 'font-size: 13px;',
                          css.td = 'border-bottom: 0px;'),               
               show.zeroinf = TRUE, show.ci = FALSE)
```

>>>>

```{r Data Wrangling}
    dat.dis <- dat.genres(dat)$dat.g %>%
          mutate(across(Classical:Metal, function(x) {if_else(x < 3, 1, 0)})) %>% 
          rowwise() %>% 
          mutate(num.dis = sum(c_across(Classical:Metal), na.rm = T)) %>% 
          ungroup() %>% 
          mutate(bin.dis = if_else(num.dis == 0, 1, 0))
    reg.dat <- dat.demog(dat) %>% 
          left_join(dat.dis) %>% 
          rename(Survey_Year = year, Political_Ideology = polviews, Education = Educ) %>%
          mutate(Black = if_else(Race == "Black", 1, 0)) %>% 
          mutate(Hisp = if_else(Race == "Hisp.", 1, 0)) %>% 
          mutate(Asian = if_else(Race == "Asian", 1, 0)) %>% 
          mutate(White = if_else(Race == "White", 1, 0)) %>%
          mutate(Mult = if_else(Race == "Mult.", 1, 0)) %>% 
          mutate(Native = if_else(Race == "Native/Other", 1, 0)) %>% 
          mutate(Woman = if_else(Gender == "Woman", 1, 0)) %>% 
          mutate(Age.n = as.numeric(Age)) %>% 
          mutate(Young = if_else(Age.n > 1 & Age.n < 5, 1, 0)) %>% 
          mutate(Old = if_else(Age.n > 9, 1, 0)) %>% 
          mutate(Educ.n = as.numeric(Education)) %>% 
          mutate(Low.Educ = if_else(Educ.n == 1, 1, 0)) %>% 
          mutate(Mid.Educ = if_else(Educ.n == 2 | Educ.n == 3, 1, 0)) %>% 
          mutate(Hi.Educ = if_else(Educ.n == 4, 1, 0)) %>% 
          mutate(polviews.n = as.numeric(Political_Ideology)) %>% 
          mutate(Moderate = if_else(polviews.n == 3 | polviews.n == 4, 1, 0)) %>% 
          mutate(Survey_Year = factor(Survey_Year, labels = c("2021", "2023", "2023"))) %>% 
          mutate(Age = factor(Age, 
                             labels = c("18 - 19", "20 - 24",
                                        "25 - 29", "30 - 34", "35 - 39", "40 - 44",
                                        "45 - 49", "50 - 54", "55 - 59", "60 - 64",
                                        "65 - 69", "70+"))) %>% 
         mutate(Education = factor(Education, labels = c("High School", "Associate", "Bachelor", "Grad/Prof."))) %>% 
         mutate(Political_Ideology = factor(Political_Ideology, 
                             labels = c("Extremely liberal", "Liberal",
                              "Slightly liberal", "Moderate",
                              "Slightly conservative", "Conservative")))
```

@@

# Regression
```{r Regression Analysis}
     m1 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Young + Old + Woman + Black + Hisp + Mult + Survey_Year, 
       data = reg.dat
       )
     m2 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult + Survey_Year, 
       data = reg.dat, weights = weight
       )
     m3 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult,       
       data = reg.dat.21, weights = weight
       )
     m4 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult,       
       data = reg.dat.23, weights = weight
       )
     m5 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult,       
       data = reg.dat.21
       )
     m6 <- zeroinfl(
       num.dis ~  Age.n + Hi.Educ + Low.Educ + polviews.n + White | 
                  Age.n + Young + Old + Woman + Black + Hisp + Mult,       
       data = reg.dat.23
       )
     tab_model(m1, m2, transform = NULL, 
               file = here("Tabs", "zinf-reg.html"), 
               auto.label = TRUE, dv.labels = c("Unweighted", "Weighted"), 
               CSS = list(css.table = 'font-size: 12px;',
                          css.td = 'border-bottom: 0px;'), 
               show.zeroinf = TRUE, show.ci = FALSE)
     tab_model(m5, m3, m6, m4, transform = NULL, 
               file = here("Tabs", "zinf-reg-appendix.html"), 
               auto.label = TRUE, dv.labels = 
                 c("Unweighted (2021)", "Weighted (2021)", 
                   "Unweighted (2023)", "Weighted (2023)"), 
               CSS = list(css.table = 'font-size: 13px;',
                          css.td = 'border-bottom: 0px;'),               
               show.zeroinf = TRUE, show.ci = FALSE)
```
